R Notebook

### 2022-04-01 R/DeaminationAnalysis.rmd
Update DeaminationAnalysis.rmd
Changed read length constraints

# Simplify the data
CPDMismatchData = lapply(CPDMismatchData, function(x) lapply(
  x, function(y) simplifyTable(filterResults(y, TRUE, 3, 20, 30))
))
sixFourMismatchData = lapply(sixFourMismatchData, function(x) lapply(
  x, function(y) simplifyTable(filterResults(y, TRUE, 3, 20, 30))
))

>>>>

# Simplify the data
CPDMismatchData = lapply(CPDMismatchData, function(x) lapply(
  x, function(y) simplifyTable(filterResults(y, TRUE, 3, 23, 31))
))
sixFourMismatchData = lapply(sixFourMismatchData, function(x) lapply(
  x, function(y) simplifyTable(filterResults(y, TRUE, 3, 23, 31))
))
